Article Title

### 2013-10-30 sections/Figure3.tex
minor
merged the graphical model into the simulation results figure.

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
In simulation, selection amongst estimators recognizes the true covariance atructure. 
{\bf A--D} are examples of true $100\times100$ covariance matrices of multivariate normal distributions used in simulations. Matrix A has no low-dimensional structure. Matrices B--D have low-dimensional structture corresponding to the respective graphical models in Fig.~2B--D.
{\bf E--H} are examples of sample covariance matrices obtained from samples of size $n=1000$ from distributions with respective true covariance matrices A--D.
{\bf I--L:} Performance evaluation of covariance estimators A, B, C, D from samples obtained from models A, B, C, D.  Excess loss $\loss{\hat\Sigma,\Sigma}-\loss{\Sigma,\Sigma}$ is only accessible with the true covariance matrix $\Sigma$ is known and zero excess loss implies absolutely correct estimation. Estimators that can represent the graphical model outperform those that cannot.  Error bars indicate the standard deviation. 
{\bf M--P:} Performance evaluation using cross-validated \emph{empirical loss} from Eq.~\ref{eq:empiricalLoss} without knowledge of true $\Sigma$. Cross-validation reproduces the same relationship between performances of the estimators.
}\label{fig:03}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\includegraphics[width=1.0\textwidth]{figures/Figure3.pdf}
\caption{
Graphical models corresponding to the low-dimensional targets of the four regularization schemes used in the paper. It assumed that all interactions are linear, \emph{i.e.}\;the mean firing rate of any neuron can be computed by a linear combination of the firing rates of other neurons and latent units.
%\textbf{A}: ``Independent.'' A population with no interactions corresponds to the diagonal covariance matrix.
%\textbf{B}: ``Latent factors.'' Observed nodes are assumed to be influenced by several latent units (``factors") but are otherwise independent.
%\textbf{C}: ``Sparse.'' Partial correlations between a subset of pairs of observed neurons, zero partial correlations between all other pairs.  
%\textbf{D}: ``Sparse+latent.''  Partial correlations between a subset of pairs of observed neurons and a few latent factors interacting with the entire population. 
{\bf E--H} are examples of true $100\times100$ covariance matrices of multivariate normal distributions used in simulations. Matrix A has no low-dimensional structure. Matrices B--D have low-dimensional structture corresponding to the respective graphical models in Fig.~2B--D.
{\bf I--L} are examples of sample covariance matrices obtained from samples of size $n=1000$ from distributions with respective true covariance matrices A--D.
{\bf M--P:} Performance evaluation of covariance estimators A, B, C, D from samples obtained from models A, B, C, D.  Excess loss $\loss{\hat\Sigma,\Sigma}-\loss{\Sigma,\Sigma}$ is only accessible with the true covariance matrix $\Sigma$ is known and zero excess loss implies absolutely correct estimation. Estimators that can represent the graphical model outperform those that cannot.  Error bars indicate the standard deviation. 
{\bf Q--T:} Performance evaluation using \emph{validated loss} from Eq.~\ref{eq:validationLoss} without knowledge of true $\Sigma$. Cross-validation reproduces the same relationship between performances of the estimators.
}\label{fig:03}
\end{figure}

### 2013-10-30 sections/Results.tex
merged the graphical model into the simulation results figure.

We considered four regularized estimators based on distinct families of low-dimensional target estimates: independent, latent factors, sparse partial correlations, and sparse partial correlations with latent factors. These target estimates are depicted graphically in Fig.~\ref{fig:02}.

\input{sections/Figure2.tex}

@@

In the first regularized estimator, the target estimate is a diagonal matrix $\hat D$.  The optimized estimate $\hat\Sigma_{\rm diag}$ is obtained by the linear \emph{shrinkage} of the unbiased estimate $\hat\Sigma_0$ toward $\hat D$ as regulated by scalar \emph{shrinkage intensity} $\lambda \in [0, 1]$:
\begin{equation}
\hat \Sigma_{\sf diag} = (1-\lambda) \hat \Sigma_0 + \lambda \hat D
\end{equation}
The diagonal target estimate expresses the idea of lack of dependence (or of linear association) between the activity of observed neurons (Fig.~\ref{fig:02}A).  If this assumption aptly describes recorded data, then strong shrinkage toward $\hat D$ will add little bias while strongly reducing the variability of the estimate.

In the second regularized estimator, the target estimate is the factor model $\hat F = \hat L \hat L^\T + \hat \Psi$ with $d$ factors so that $\hat L$ is the $p\times d$ matrix of \emph{factor loadings} and the diagonal matrix $\hat \Psi$ contains the independent variances of each neuron.
Then the estimate is 
\begin{equation}
\hat \Sigma_{\sf factor} = (1-\lambda) \hat \Sigma_0 + \lambda \hat F,
\end{equation}
This estiamtor has two hyperparameters: the number of factors $d$ and shrinkage intensity $\lambda$. The target estimate $\hat F$ expresses the assumption that the fluctuations in population activity are driven by relatively small number of latent factors that affect many cells while direct interactions between cells are insignificant (Fig.~\ref{fig:02}B).

The third estimator is based on the assumption that only a small fraction of pairs of neurons should have nonzero partial correlations.  While usual correlations are calculated from the marginal distribution without conditioning on all the other neurons, the partial correlation between a pair of neurons expresses the correlation of their activity conditioned on the activity of all the other cells.  If cells only exert linear effects on each other and all neurons are visible, partial correlations express the direct interactions between neurons. Therefore, this estimator is biased toward the assumption that correlations arise due to interactions between a subset of pairs of recorded neurons (Fig.~\ref{fig:02}C). When the partial correlation between a pair of neurons is zero, then the corresponding element of the inverse of the covariance matrix (often referred to as the \emph{precision matrix} or \emph{concentration matrix}) must be zero as well. Then the estimator is 
\begin{equation}
\hat\Sigma_{\sf sparse} = \hat S_\rho^{-1}
\end{equation}
where $\hat S\rho$ is a sparse matrix with a large fraction of zeros in its off-diagonal elements. The  one hyperparameter $\rho$ expresses the sparsity (fraction of off-diagonal zeros) in $\hat\Sigma_\rho$.

Finally, we consider a fourth estimator, which allows for both common latent factors interacting with all recorded neurons and sparse interactions between the recorded neurons (Fig.~\ref{fig:02}D). This estimator has the form
\begin{equation}
\hat\Sigma_{\sf sparse+latent} = (\hat S_\rho + \hat L\hat L^\T)^{-1},
\end{equation}
where, as above, $\hat S_\rho$ is a sparse matrix and $\hat L$ is a $d\times p$ matrix of factor loadings. The estimator has two hyperparameters: the number of latent units $d$ and the sparsity of the sparsity of local interactions $\rho$.

>>>>

We considered four regularized estimators based on distinct families of low-dimensional target estimates: independent, latent factors, sparse partial correlations, and sparse partial correlations with latent factors. These target estimates are depicted graphically in Fig.~\ref{fig:03}A-D.

@@

In the first regularized estimator, the target estimate is a diagonal matrix $\hat D$.  The optimized estimate $\hat\Sigma_{\rm diag}$ is obtained by the linear \emph{shrinkage} of the unbiased estimate $\hat\Sigma_0$ toward $\hat D$ as regulated by scalar \emph{shrinkage intensity} $\lambda \in [0, 1]$:
\begin{equation}
\hat \Sigma_{\sf diag} = (1-\lambda) \hat \Sigma_0 + \lambda \hat D
\end{equation}
The diagonal target estimate expresses the idea of lack of dependence (or of linear association) between the activity of observed neurons (Fig.~\ref{fig:03}A).  If this assumption aptly describes recorded data, then strong shrinkage toward $\hat D$ will add little bias while strongly reducing the variability of the estimate.

In the second regularized estimator, the target estimate is the factor model $\hat F = \hat L \hat L^\T + \hat \Psi$ with $d$ factors so that $\hat L$ is the $p\times d$ matrix of \emph{factor loadings} and the diagonal matrix $\hat \Psi$ contains the independent variances of each neuron.
Then the estimate is 
\begin{equation}
\hat \Sigma_{\sf factor} = (1-\lambda) \hat \Sigma_0 + \lambda \hat F,
\end{equation}
This estiamtor has two hyperparameters: the number of factors $d$ and shrinkage intensity $\lambda$. The target estimate $\hat F$ expresses the assumption that the fluctuations in population activity are driven by relatively small number of latent factors that affect many cells while direct interactions between cells are insignificant (Fig.~\ref{fig:03}B).

The third estimator is based on the assumption that all correlations are the result of direct linear interactions between a fraction of observed cell pairs.  This assumption is enforced by reducing to zero the majority of pairwise \emph{partial correlations} in the recorded population. While usual correlations are calculated from the marginal distribution without conditioning on all the other neurons, the partial correlation expresses the pairwise correlation conditioned on the activity of all the other cells.  If cells only exert linear effects on each other and all neurons are visible, partial correlations express the direct interactions between neurons. Therefore, this estimator is biased toward the assumption that correlations arise due to interactions between a subset of pairs of recorded neurons (Fig.~\ref{fig:03}C). When the partial correlation between a pair of neurons is zero, then the corresponding element of the inverse of the covariance matrix (often referred to as the \emph{precision matrix} or \emph{concentration matrix}) must be zero as well. Then the estimator is 
\begin{equation}
\hat\Sigma_{\sf sparse} = \hat S^{-1}
\end{equation}
where $\hat S$ is a sparse matrix with a large fraction of zeros in its off-diagonal elements. The  one hyperparameter $\rho$ expresses the sparsity (fraction of off-diagonal zeros) in $\hat\Sigma$.

Finally, we consider a fourth estimator, which allows for both common latent factors interacting with all recorded neurons and sparse interactions between the recorded neurons (Fig.~\ref{fig:03}D). This estimator has the form
\begin{equation}
\hat\Sigma_{\sf sparse+latent} = (\hat S - \hat L\hat L^\T)^{-1},
\end{equation}
where, as above, $\hat S$ is a sparse matrix and $\hat L$ is a $d\times p$ matrix of factor loadings. The estimator has two hyperparameters: the number of latent units $d$ and the sparsity of the sparsity of local interactions $\rho$.
